|

### 2023-01-16 manuscript/manuscript_1.0.Rmd
Figures directly included in the Rmardown document. Need to do this only ofr the last figure

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,cache=TRUE,warnings=FALSE)
require(png)
require(here)
source(here("../R_files/posPlots.r"))
source(here("AccFunc.r"))
```

@@

A somewhat ignored component of communication systems, in the context 
of aggressive interactions, is the cognitive aspects of the receiver module. 
Theoretical models often assume that Communication systems relying on badges of 
status to have reaction norms as their 
mechanistic underpinning [@botero_Evolution_2010], with 
individuals using their own quality and the opponent's badge to determine 
whether to aggressively engage in contest. Reaction norms 
allow individuals to respond to the available information without a big
cognitive burden. That is at least in contrast to other information processing 
mechanisms like individual recognition. With individual recognition 
individuals associate cue of their peers to their quality. These association 
must be learn thoughout individuals lifes, thus it has the usual 
cognitive requirements of an associative learning process. An alternative view 
of badges of status is that individuals learn 
to react to them based on their experiences [@guilford_Receiver_1991], 
which would imply that receivers must learn to associate signals with 
the fighting ability of bearers just as in systems based on individual 
recognition. In cases where badges of status vary quantitatively 
(e.g. in size or intensity), fighting ability may increase monotonically 
with attributes of the badge and would be reinforced by every interaction, 
so in principle learning would be faster than in systems involving individual 
recognition in which the association between signals and their meaning would 
vary depending on the interacting partners. In any case, learning could be 
a central cognitive mechanism in both types of communication systems, 
but the role of learning in these contexts has not been thoroughly 
explored in the empirical nor theoretical literature.

@@

We model the evolution of signals of quality in the context of agonistic 
interactions. For simplicity we consider a population of haploid 
individuals with non-overlapping generations. Individuals are born 
every generation with a level of quality ($Q_i$, where $i$ is subscript 
of the population vector of size $N$) given by a number between zero and one, 
which is drawn from a truncated normal distribution 
$N(\mu = 0.5,\sigma)$. An individual with quality $0$ has the lowest RHP, 
while an individual with quality $1$ has the highest. As part of 
development processes individuals produce a morphological signal (badge), 
the size of such depends on their level 
of quality according to a reaction norm given by 
$B_i=1/(1+e^{\alpha_i-\beta_i Q_i})$; where are $\alpha_i$ and 
$\beta_i$ are individual specific traits that determine the shape of 
the reaction norm (Fig. \ref{fig:model-struc} A). Variation in $\alpha_i$ 
and $\beta_i$ means individuals can have either uninformative (flat) or 
informative (logistic) norms. The size of the signal is constrained 
between zero and one. We assume different values of these traits 
are given by different alleles, and are inherited from mother to offspring. 
Unless, with a small probability, mutation changes the allelic value 
of the offspring. After birth individuals go through a round of 
viability selection. Individual specific survival probability is 
given by $s_i=1/(1+e^{-k_1-k_2(Q_i-B_i)})$. Where $k_1$ and $k_2$ are parameter 
values determining the shape of the survival function. 
Importantly, if $k_2=0$ survival probability is independent of quality, 
while if $k_2>0$ lower quality individuals pay a higher price for similar-sized 
badge, fulfilling the core assumption of the handicap principle 
[@botero_Evolution_2010; @grafen_Biological_1990; @johnstone_Badges_1993].

@@

The decision of whether to escalate a fight against an interacting 
partner can be dependent on the size of the partner's badge, 
the actual dependency is determined by the focal´s experiences 
through a learning process. We implement learning using 
the actor-critic approach from reinforcement learning theory [RL; @sutton_Reinforcement_2018;@quinones_Reinforcement_2019; @leimar_Learning_2019].
Individuals estimate the reward (pay-off) expected from  interacting 
with partners of different badge sizes (the critic in RL terminology). 
After every interaction they update the estimate of reward proportionally 
to the difference between their current estimate and the observed 
reward (prediction error $\delta$) and to the speed of learning 
($\mathrm{A}$). Furthermore, they express different probabilities of 
retreating (attacking) depending on the badge size of their opponent 
(the actor in RL). They update the probability of 
retreating (attacking)  up or down depending on whether retreating 
(attacking) leads to an increase in the reward estimation. 
So, if a focal individual decides to escalate a fight against 
an individual with small badge, and that leads to an increase in 
the reward estimation, the focal individual will increase the probability 
of escalating fights with individuals of small badges in the future. 
Given that badge size is a real number between 0 and 1, there are infinitely 
many badge sizes. Thus, the reward estimation, as well as the probability 
of retreating (escalating), must be generalized across different values. 
To implement generalization we use the linear function approximation 
method based on radial basis functions [@sutton_Reinforcement_2018]. 
Specifically, we pick $c$ feature centres, which are evenly spaced values 
along the badge size interval ([0,1]). Each one of these features centres 
is associated with a weight for reward estimation and tendency to play 
retreat in a given interaction. The reward estimation and the tendency 
to retreat are calculated (in every interaction) as the sum of the weights 
associated with each feature, weighted by the response 
triggered by the feature (Fig. \ref{fig:model-struc} B, dots 
represent the feature weights) The response of each feature centre 
diminishes as a Gaussian function  with the distance between the 
feature centre and the badge size of 
the partner (Fig. \ref{fig:model-struc} B, grey line). Formally the 
reward estimation $\hat{R}$ when the focal individual ($i$) faces 
individual $j$ is given by,
\
\begin{equation}
\hat{R}_{ij} =  \sum_{z=1}^{c} x_z e^{(-\frac{|B_i-c_z|}{2\theta^2})} 
\end{equation}

@@

```{r model-struc,echo=FALSE,fig.width=8,fig.align='center',fig.height=8,fig.show='hold',fig.cap= "Model of communication in the context of aggressive interactions. In A the sender code: a reaction norm determines how the badge size is determined by the quality of the individual. Red shows an informative reaction norm, while the blue shows a uninformative reaction norm. B the receiver code: individuals have a behavioral reaction norm that determines their probability of retreating (black line). The reaction norm arises from generalizing the information from the feature weights (black dots). Generalization is represented by the grey line and its axis, which shows the response triggered by the fourth feature diminishes as the value evaluated is further from the feature center. The learning process moves the feature weights (black dots) up or down depending on whether that leads to an increase in the estimated reward. In C and D, effect of learning on the receiver strategy. Receivers in C face signallers with uninformative reaction norms (blue line in A), while in D they face signallers with informative reaction norms (red line in A). Colour scale in C (applies also for D) indicates the quality of the individual"}

@@

honestBig<-readPNG(here("Images/cart_honestBig.png"))
honestSmall<-readPNG(here("Images/cart_honestSmall.png"))
dishonest<-readPNG(here("Images/cart_dishonest.png"))
par(plt=posPlot(numplotx = 2,idplotx = 1,numploty = 1,idploty = 1,upboundx = 91),
    las=1,mfrow=c(2,1))
  rangPars<-data.frame(honest=c(4,2),dishonest=c(0,0))
 rangQual<-seq(0,1,by = 0.01)
 linesSender<-sapply(rangPars,function(x)logist(rangQual,alpha = x[2],beta = x[1]))
 plot(0,0,type="l",xlab="",xlim=c(0,1),
      ylab ="",cex.lab=1,lwd=2,col="grey",cex.axis=1,ylim=c(0,1.1),xaxt="n")
 axis(1)
 text(x = 0.08,y=1.05,"A",cex = 1.5)
 mtext("Quality",1,line = 2,cex = 1,las = 0)
 matlines(x=rangQual,y=linesSender,lwd=4,col=colRuns,lty=1)
 mtext("Badge size",2,line = 2.3,cex = 1,las = 0)
 # include bird cartoons
 rasterImage(honestBig,0.75,0.87,0.95,1.07)
 rasterImage(honestSmall,0.05,0.01,0.25,0.21)
 rasterImage(dishonest,0.75,0.5,0.95,0.7)
 rasterImage(dishonest,0.05,0.5,0.25,0.7)
 # legend("left",legend=rangeBeta,col=colRuns,lwd=3,title = expression(beta),cex=2,bty="n")

@@

rangx<-seq(0,1,by=0.01)
  dataIndsAct<-sapply(as.list(tempPop[nInteract==behavTime,indId]),
                      function(x){x=
                        logist(totRBF(rangx,
                                      centers,sigSquar,
                                      as.double(
                                        tempPop[(nInteract==behavTime
                                                 &indId==x)
                                                # &(Quality>0.8&Quality<1)
                                                ,.SD,
                                                .SDcol=grep("WeightAct",
                                                            names(tempPop),
                                                            value = TRUE)
                                                ])),alpha = 0,beta = 1)})
  # par(plt=posPlot(numploty = 4,numplotx = 4,idploty = 2,idplotx = 1))
  par(plt=posPlot(numploty = 1,numplotx = 2,idploty = 1,idplotx = 1,upboundx = 91))
matplot(x=rangx,y=dataIndsAct,type='l',xlab="",ylab="prob. retreat",
          xaxt="s",yaxt="s",lty = 1,
          col=paletteMeans(100)[
            findInterval(tempPop[nInteract==1700,Quality],colorbreaksQual)],
          lwd=0.5,ylim=c(0,1.1))
text(x = 0.08,y=1.05,"C",cex = 1.5)
par(new=FALSE)
color.bar.aeqp(paletteMeans(100),min =min(colorbreaksQual),
               max = max(colorbreaksQual),nticks = 3,
               cex.tit = 0.9,title = "quality",
               numplotx = 20,numploty = 10,idplotx =9,idploty = 2)

@@

rangx<-seq(0,1,by=0.01)
  dataIndsAct<-sapply(as.list(tempPop[nInteract==behavTime,indId]),
                      function(x){x=
                        logist(totRBF(rangx,
                                      centers,sigSquar,
                                      as.double(
                                        tempPop[(nInteract==behavTime
                                                 &indId==x)
                                                # &(Quality>0.8&Quality<1)
                                                ,.SD,
                                                .SDcol=grep("WeightAct",
                                                            names(tempPop),
                                                            value = TRUE)
                                                ])),alpha = 0,beta = 1)})
  # par(plt=posPlot(numploty = 4,numplotx = 4,idploty = 2,idplotx = 1))
  par(plt=posPlot(numploty = 1,numplotx = 2,idploty = 1,idplotx = 2,upboundx = 91)
      ,new=TRUE,xpd=TRUE)
matplot(x=rangx,y=dataIndsAct,type='l',xlab="",ylab="",
          xaxt="s",yaxt="n",lty = 1,
          col=paletteMeans(100)[
            findInterval(tempPop[nInteract==1700,Quality],colorbreaksQual)],
          lwd=0.5,ylim=c(0,1.1))
text(x = 0.08,y=1.05,"D",cex = 1.5)
text(x = -0.1,y = -0.23,labels = "Badge size")

@@

```{r handicap,echo=FALSE,out.width='90%',fig.align='center',fig.show='hold',fig.cap="Evolution of the badge size as a handicap mediated by learning. Middle panels show the evolutionary dynamics of the sender code. On the left, changes in the distribution of values for the intercept of the reaction norm ($\\alpha$); on the right changes in the distribution of the slope ($\\beta$). Dashed lines in both panels show the mean of the distribution. Grey lines show the generation time corresponding to the panels above and below showing the sender and receiver code. In the panels above, the reaction norms correspond to individuals in the population after the interaction round. Color scale indicates quality just as in Fig. \\ref{fig:model-struc}. In the panels below, colors represent a cluster clasification performed by the k-means algorithm" }

knitr::include_graphics(here("Simulations","betCostEvol1_","evolDyn0_betCost5.png"))

@@

knitr::include_graphics(here("Simulations","nIntGroupNormQual_","evolDyn7_nIntGroup2000.png"))

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,cache=TRUE,warnings=FALSE)
require(png)
require(here)
source(here("../R_files/posPlots.r"))
source(here("AccFunc.r"))
```

@@

A somewhat ignored component of communication systems, in the context 
of aggressive interactions, is the cognitive aspects of the receiver module. 
Theoretical models often assume that communication systems relying on badges of 
status to have reaction norms as their 
mechanistic underpinning [@botero_Evolution_2010], with 
individuals using their own quality and the opponent's badge to determine 
whether to aggressively engage in contest. Reaction norms 
allow individuals to respond to the available information without a big
cognitive burden. That is at least in contrast to other information processing 
mechanisms like individual recognition. With individual recognition 
individuals associate cue of their peers to their quality. These association 
must be learn thoughout individuals lifes, thus it has the usual 
cognitive requirements of an associative learning process. An alternative view 
of badges of status is that individuals learn 
to react to them based on their experiences [@guilford_Receiver_1991], 
which would imply that receivers must learn to associate signals with 
the fighting ability of bearers just as in systems based on individual 
recognition. In cases where badges of status vary quantitatively 
(e.g. in size or intensity), fighting ability may increase monotonically 
with attributes of the badge and would be reinforced by every interaction, 
so in principle learning would be faster than in systems involving individual 
recognition in which the association between signals and their meaning would 
vary depending on the interacting partners. In any case, learning could be 
a central cognitive mechanism in both types of communication systems, 
but the role of learning in these contexts has not been thoroughly 
explored in the empirical nor theoretical literature.

@@

We model the evolution of signals of quality in the context of agonistic 
interactions. For simplicity we consider a population of haploid 
individuals with non-overlapping generations. Individuals are born 
every generation with a level of quality ($Q_i$, where $i$ is subscript 
of the population vector of size $N$) given by a number between zero and one, 
which is drawn from a truncated normal distribution 
$N( 0.5,\sigma)$. An individual with quality $0$ has the lowest RHP, 
while an individual with quality $1$ has the highest. As part of 
development processes individuals produce a morphological signal (badge), 
the size of such depends on their level 
of quality according to a reaction norm given by 
$B_i=1/(1+e^{\alpha_i-\beta_i Q_i})$; where $\alpha_i$ and 
$\beta_i$ are individual specific traits that determine the shape of 
the reaction norm (Fig. \ref{fig:model-struc} A). Variation in $\alpha_i$ 
and $\beta_i$ means individuals can have either uninformative (flat) or 
informative (logistic) norms. The size of the signal is constrained 
between zero and one. We assume different values of these traits 
are given by different alleles, and are inherited from mother to offspring. 
Unless, with a small probability ($\mu$), mutation changes the allelic value 
of the offspring by an amount taken from a normal distribution $N(0,\sigma_\mu)$.
After birth individuals go through a round of 
viability selection. Individual specific survival probability is 
given by $s_i=1/(1+e^{-k_1-k_2(Q_i-B_i)})$. Where $k_1$ and $k_2$ are parameter 
values determining the shape of the survival function. 
Importantly, if $k_2=0$ survival probability is independent of quality, 
while if $k_2>0$ lower quality individuals pay a higher price for similar-sized 
badge, fulfilling the core assumption of the handicap principle 
[@botero_Evolution_2010; @grafen_Biological_1990; @johnstone_Badges_1993].

@@

The decision of whether to escalate a fight against an interacting 
partner can be dependent on the size of the partner's badge, 
the actual dependency is determined by the focal´s experiences 
through a learning process. We implement learning using 
the actor-critic approach from reinforcement learning (RL) theory [@sutton_Reinforcement_2018;@quinones_Reinforcement_2019; @leimar_Learning_2019].
Individuals estimate the reward (pay-off) expected from  interacting 
with partners of different badge sizes (the critic in RL terminology). 
After every interaction they update the estimate of reward proportionally 
to the difference between their current estimate and the observed 
reward (prediction error $\delta$) and to the speed of learning 
($\mathrm{A}$). Furthermore, they express different probabilities of 
retreating (attacking) depending on the badge size of their opponent 
(the actor in RL). They update the probability of 
retreating (attacking)  up or down depending on whether retreating 
(attacking) leads to an increase in the reward estimation. 
So, if a focal individual decides to escalate a fight against 
an individual with small badge, and that leads to an increase in 
the reward estimation, the focal individual will increase the probability 
of escalating fights with individuals of small badges in the future. 
Given that badge size is a real number between 0 and 1, there are infinitely 
many badge sizes. Thus, the reward estimation, as well as the probability 
of retreating (escalating), must be generalized across different values. 
To implement generalization we use the linear function approximation 
method based on radial basis functions [@sutton_Reinforcement_2018]. 
Specifically, we pick $c$ feature centres, which are evenly spaced values 
along the badge size interval ([0,1]). Each one of these features centres 
is associated with a weight for reward estimation and tendency to play 
retreat in a given interaction. The reward estimation and the tendency 
to retreat are calculated (in every interaction) as the sum of the weights 
associated with each feature, weighted by the response 
triggered by the feature (Fig. \ref{fig:model-struc} B, dots 
represent the feature weights) The response of each feature centre 
diminishes as a Gaussian function  with the distance between the 
feature centre and the badge size of 
the partner (Fig. \ref{fig:model-struc} B, grey line). Formally the 
reward estimation $\hat{R}$ when the focal individual ($i$) faces 
individual $j$ is given by,
\
\begin{equation}
\hat{R}_{ij} =  \sum_{z=1}^{c} x_z e^{(-\frac{|B_i-c_z|}{2\theta^2})} 
\end{equation}

@@

```{r model-struc,echo=FALSE,warning=FALSE,fig.width=8,fig.align='center',fig.height=7,fig.show='hold',fig.cap= "Model of communication in the context of aggressive interactions. In A the sender code: a reaction norm determines how the badge size is determined by the quality of the individual. Red shows an informative reaction norm, while the blue shows a uninformative reaction norm. B the receiver code: individuals have a behavioral reaction norm that determines their probability of retreating (black line). The reaction norm arises from generalizing the information from the feature weights (black dots). Generalization is represented by the grey line and its axis, which shows the response triggered by the fourth feature diminishes as the value evaluated is further from the feature center. The learning process moves the feature weights (black dots) up or down depending on whether that leads to an increase in the estimated reward. In C and D, effect of learning on the receiver strategy. Receivers in C face signallers with uninformative reaction norms (blue line in A), while in D they face signallers with informative reaction norms (red line in A). Colour scale in C (applies also for D) indicates the quality of the individual"}

@@

library(dplyr)
honestBig<-readPNG(here("Images/cart_honestBig.png"))
honestSmall<-readPNG(here("Images/cart_honestSmall.png"))
dishonest<-readPNG(here("Images/cart_dishonest.png"))
par(plt=posPlot(numplotx = 2,idplotx = 1,numploty = 1,idploty = 1,upboundx = 91),
    las=1,mfrow=c(2,1),mgp=c(2,0.7,0))
  rangPars<-data.frame(honest=c(4,2),dishonest=c(0,0))
 rangQual<-seq(0,1,by = 0.01)
 linesSender<-sapply(rangPars,function(x)logist(rangQual,alpha = x[2],beta = x[1]))
 plot(0,0,type="l",xlab="",xlim=c(0,1),
      ylab ="",cex.lab=1,lwd=2,col="grey",cex.axis=1,ylim=c(0,1.1),xaxt="n")
 axis(1)
 text(x = 0.08,y=1.05,"A",cex = 1.5)
 mtext("Quality",1,line = 2,cex = 1,las = 0)
 matlines(x=rangQual,y=linesSender,lwd=4,col=colRuns,lty=1)
 mtext("Badge size",2,line = 2.3,cex = 1,las = 0)
 # include bird cartoons
 rasterImage(honestBig,0.75,0.87,0.95,1.07)
 rasterImage(honestSmall,0.05,0.01,0.25,0.21)
 rasterImage(dishonest,0.75,0.5,0.95,0.7)
 rasterImage(dishonest,0.05,0.5,0.25,0.7)
 # legend("left",legend=rangeBeta,col=colRuns,lwd=3,title = expression(beta),cex=2,bty="n")

@@

rangx<-seq(0,1,by=0.01)
  dataIndsAct<-sapply(as.list(tempPop[nInteract==behavTime,indId]),
                      function(x){x=
                        logist(totRBF(rangx,
                                      centers,sigSquar,
                                      as.double(
                                        tempPop[(nInteract==behavTime
                                                 &indId==x)
                                                # &(Quality>0.8&Quality<1)
                                                ,.SD,
                                                .SDcol=grep("WeightAct",
                                                            names(tempPop),
                                                            value = TRUE)
                                                ])),alpha = 0,beta = 1)})
  # par(plt=posPlot(numploty = 4,numplotx = 4,idploty = 2,idplotx = 1))
  par(plt=posPlot(numploty = 1,numplotx = 2,idploty = 1,idplotx = 1,upboundx = 91))
matplot(x=rangx,y=dataIndsAct,type='l',xlab="",ylab="prob. retreat",
          xaxt="s",yaxt="s",lty = 1,
          col=paletteMeans(100)[
            findInterval(tempPop[nInteract==1700,Quality],colorbreaksQual)],
          lwd=3,ylim=c(0,1.1))
text(x = 0.08,y=1.05,"C",cex = 1.5)
par(new=FALSE)
color.bar.aeqp(paletteMeans(100),min =min(colorbreaksQual),
               max = max(colorbreaksQual),nticks = 3,
               cex.tit = 0.9,title = "quality",
               numplotx = 20,numploty = 10,idplotx =9,idploty = 2)

@@

rangx<-seq(0,1,by=0.01)
  dataIndsAct<-sapply(as.list(tempPop[nInteract==behavTime,indId]),
                      function(x){x=
                        logist(totRBF(rangx,
                                      centers,sigSquar,
                                      as.double(
                                        tempPop[(nInteract==behavTime
                                                 &indId==x)
                                                # &(Quality>0.8&Quality<1)
                                                ,.SD,
                                                .SDcol=grep("WeightAct",
                                                            names(tempPop),
                                                            value = TRUE)
                                                ])),alpha = 0,beta = 1)})
  # par(plt=posPlot(numploty = 4,numplotx = 4,idploty = 2,idplotx = 1))
  par(plt=posPlot(numploty = 1,numplotx = 2,idploty = 1,idplotx = 2,upboundx = 91)
      ,new=TRUE,xpd=TRUE)
matplot(x=rangx,y=dataIndsAct,type='l',xlab="",ylab="",
          xaxt="s",yaxt="n",lty = 1,
          col=paletteMeans(100)[
            findInterval(tempPop[nInteract==1700,Quality],colorbreaksQual)],
          lwd=3,ylim=c(0,1.1))
text(x = 0.08,y=1.05,"D",cex = 1.5)
text(x = -0.1,y = -0.25,labels = "Badge size")

@@

```{r handicap,echo=FALSE,out.width='100%',fig.height=6,fig.align='center',fig.show='hold',fig.cap="Evolution of the badge size as a handicap mediated by learning. Middle panels show the evolutionary dynamics of the sender code. On the left, changes in the distribution of values for the intercept of the reaction norm ($\\alpha$); on the right changes in the distribution of the slope ($\\beta$). Dashed lines in both panels show the mean of the distribution. Grey lines show the generation time corresponding to the panels above and below showing the sender and receiver code. In the panels above, the reaction norms correspond to individuals in the population after the interaction round. Color scale indicates quality just as in Fig. \\ref{fig:model-struc}. In the panels below, colors represent a cluster clasification performed by the k-means algorithm" ,warning=FALSE}

scenario<-"betCostEvol4"#"alphaAct"#"nIntGroupNormQual"#

# Load files -------------------------------------------------------------------
# Project folder
listTest<-list.files(here("Simulations",paste0(scenario,"_")),full.names = TRUE)
evolList<-grep("evolLearn",listTest,value=TRUE)
indList<-grep("indLearn",listTest,value=TRUE)
paramName<-list.files(here("Simulations",paste0(scenario,"_")))
# paramName<-list.files(extSimsDir,full.names = TRUE)
paramName<-grep(".json",paramName,value=TRUE) %>% grep(pattern = "*5_*",value = TRUE)

param<-fromJSON(here("Simulations",paste0(scenario,"_"),paramName[2]))
  # fromJSON(paramName[1])
val<-2
fileId<-val
evolList_runs<-grep(paste0(param$namParam,param$rangParam),
                    evolList,value =TRUE)
indList_runs<-grep(paste0(param$namParam,param$rangParam),
                   indList,value =TRUE)
evol<-do.call(rbind,lapply(evolList_runs,fread))
pop<-do.call(rbind,lapply(indList_runs, fread))

Valpar<-param$rangParam

nampar<-param$namParam

nCenters<-param$nCenters
sigSquar<-param$sigSq

# Aesthetic paremeters ---------------------------------------------------------

## Calculate clustering for all generations  -------------------

runChoi<-1
# Choose which interaction to visualize
# lastInt<-tail(pop[,unique(nInteract)],4)[2]
# # pop[,max(nInteract),by=.(seed,time)][,min(V1)]
# # to get last interaction: tail(pop[,unique(nInteract)],1)
# 
# popOneInd<-pop[nInteract==lastInt]
# vars<-c("alpha","beta","Badge")
# # ,"Badge",grep("WeightAct",names(popFinal),value = TRUE))
# popOneInd$idClust<-get_clusters(popOneInd,vars,k.max = 5,
#                                 Bsamples =500,iterMax = 500)
# clusSummary<-popOneInd[,.(meanAlph=mean(alpha),meanBet=mean(beta)),
#                        by=.(idClust,time,seed)]
# clusSummary[,orderClus:=0]
# invisible(capture.output(
#   for(i in 1:dim(clusSummary)[1]){
#   set(clusSummary,i,6L,match(clusSummary[i,meanAlph],
#         sort(clusSummary[time==clusSummary[i,time]&
#                            seed==clusSummary[i,seed]]$meanAlph)))
# }
# ))
# 
# 
# popOneInd<-merge(popOneInd,clusSummary,all = TRUE)
# 
# fwrite(popOneInd,file = here("Simulations",paste0(scenario,"_"),
#                              paste0("popOneInd",nampar,Valpar,".txt")))

popOneInd<-fread(here("Simulations",paste0(scenario,"_"),
                             paste0("popOneInd",nampar,Valpar,".txt")))

# Get stats from the evolutionary simulations ----------------------------------
# names(evol)

cols<-c("freqGenHawks","freqGenDove",  "freqGenEval",  #"freqGenLearn",
        "freqFenHawks", "freqFenDoves", "freqHH", "freqHD", "freqDD", "meanCue",
        "meanAlpha", "meanBeta",
        #"meanFit", #"meanInitCrit", "sdInitCrit", "meanInitAct", "sdInitAct",
        "WeightAct_0","WeightCrit_0",
        "WeightAct_1","WeightCrit_1","WeightAct_2",  "WeightCrit_2",
        "WeightAct_3",  "WeightCrit_3", "WeightAct_4",  "WeightCrit_4",
        "WeightAct_5","WeightCrit_5")

my.summary<- function(x) list(mean = mean(x), lowIQR = fivenum(x)[2], 
                              upIQR = fivenum(x)[4])

evolStats<-evol[, as.list(unlist(lapply(.SD, my.summary))), 
                .SDcols = cols,by=time]

## Plot mean and IQRs among individuals for each replicate --------------------

# get the trajectories for individual runs
traitsTrajs<-dcast(evol,time~seed,
                   value.var = c("meanAlpha","meanBeta",
                                 #"meanInitCrit",#"meanFit",
                                 # "meanInitAct","sdInitCrit","sdInitAct",
                                 "sdAlpha","sdBeta","freqHH",
                                 "freqHD","freqDD"))

finReps<-evol[time==max(time),seed]

genstoPrint<-round(seq(1,length(unique(evolStats$time)),length.out = 5))[2:5]

# Evolutionary dynamics for alpha - intercept of the sender --------------------------------------------
cexAxis<-1

par(plt=posPlot(numploty = 3,idploty = 2,numplotx = 2,idplotx = 1,
                lowboundx = 8, title = TRUE,lowboundy = 10,
                upboundy = 90),
    mfrow=c(1,1), xaxt="s",las=1,mgp=c(2,0.5,0))

evolDist(indData = pop[seed==runChoi],variable = "alpha",nbins = 10,pal = pal_dist,
         nlevels=10,cexAxis = cexAxis,xlab="",ylab = "",xaxt="n",yaxt = "s",
         ylim = range(pop[seed==runChoi,alpha])*c(2,1.4),xlim=c(0,22000))

mtext(text = "Trait value",cex = cexAxis,line = 1,side = 2,las=0)
legend("top",legend = c(expression(alpha[s])),col=colGenesLin[1],lwd=2,
       bty = "n",cex=cexAxis)

axis(side=1,padj = -2,at = axTicks(1)[2:(length(axTicks(1)))],
     labels = axTicks(1)[2:(length(axTicks(1)))]/1000,cex.axis=cexAxis,
     hadj = 1.3,line = -0.5,tick = FALSE)

# grey lines to show the generations shown in the upper and lower panels

matlines(x=matrix(rep(evolStats[genstoPrint,time],each=2),nrow=2),
         y=matrix(rep(c(-2,3),4),nrow = 2),lty=1,col = "grey",lwd=2)

# Variation among individuals

matlines(x=traitsTrajs[,time],
         y=traitsTrajs[,.SD,
                       .SDcol=paste0(c("meanAlpha_"),runChoi)],
         col=colGenesLin,lty = 2,type="l",lwd=5)

par(plt=posPlot(numploty = 3,idploty = 2,numplotx = 2, idplotx = 2,
                lowboundx = 8, title = TRUE,lowboundy = 10,
                upboundy = 90),
    xaxt="s",las=1,new=TRUE)

evolDist(indData = pop[seed==runChoi],variable = "beta",nbins = 10,pal = pal_dist,
         nlevels=10,cexAxis = 1.5,xlab="",ylab = "",xaxt="n",yaxt = "n",
         ylim = range(pop[seed==runChoi,beta])*c(2,1.4),xlim=c(0,22000))
legend("top",legend = c(expression(beta[s])),cex=cexAxis,
       col=colGenesLin[2],lwd=2,bty = "n")
# grey lines to show the generations shown in the upper and lower panels
matlines(x=matrix(rep(evolStats[genstoPrint,time],each=2),nrow=2),
         y=matrix(rep(c(-2,6),4),nrow = 2),lty=1,col = "grey",lwd=2)

axis(side=1,padj = -2,at = axTicks(1)[2:(length(axTicks(1)))],
     labels = axTicks(1)[2:(length(axTicks(1)))]/1000,cex.axis=cexAxis,
     hadj = 1.3,line = -0.5,tick = FALSE)

axis(4,cex.axis=cexAxis)

matlines(x=traitsTrajs[,time],
         y=traitsTrajs[,.SD,
                       .SDcol=paste0(c("meanBeta_"),runChoi)],
         col=colGenesLin[2],lty = 2,type="l",lwd=4)

# Choose time range
gen2plot<-round(seq(1,length(unique(evolStats$time)),length.out = 5))[2:5]
# Plor the actor
seqYax<-c("s",rep("n",3))
# seqYlabUp<-c("Badge",rep("",3))
seqYlabUp<-c("P(dove)",rep("",3))
seqYlabDown<-c("Badge",rep("",3))
seqXlabDown<-c("","Quality","")#paste0("seed: ",runChoi))
seqXlabUp<-c("","Badge","")
rangQual<-seq(0,1,length.out = 50)
interv<-1/(nCenters-1)
centers<-interv*seq(0,nCenters-1)
rangx<-seq(0,1,length=50)
count<-0
for(genC in genstoPrint){
  count<-count+1
  par(plt=posPlot(numplotx = 4,numploty = 3,idplotx = count,idploty = 3,
                  lowboundx = 8, title = TRUE,lowboundy = 10,
                  upboundy = 90),
      xaxt="s",las=1,new=TRUE)
  weightsAct<-as.double(evol[(time==unique(time)[genC])&seed==runChoi,.SD,
                             .SDcols=grep("WeightAct",
                                          names(evol),value = TRUE)])
  tempPop<-popOneInd[(time==unique(time)[genC]&seed==runChoi),.SD[.N],
               .SDcol=c(grep("WeightAct",
                             names(evol),value = TRUE),"Quality","alpha","beta",
                        "orderClus"),
               by=indId]

  randInds<-sample(tempPop$indId, length(tempPop$indId), replace = FALSE)

  dataIndAct<-sapply(as.list(tempPop[indId %in%randInds,indId]),
                     function(x){x=
                       logist(totRBF(rangx,
                                     centers,sigSquar,
                                     as.double(
                                       tempPop[indId==x,.SD,
                                               .SDcol=grep("WeightAct",
                                                           names(tempPop),
                                                           value = TRUE)
                                               ])),alpha=0,beta = 1)})
  matplot(x=rangx,y=dataIndAct,
          yaxt=seqYax[count],ylab="",xlab="",type="l",cex.lab=cexAxis,
          lwd=2,xaxt="n",ylim=c(-0.06,1),col = paletteMeans(100)[
            findInterval(tempPop[,Quality],colorbreaksQual)],lty = 1,
          cex.axis=cexAxis)
  axis(side = 3,cex.axis=cexAxis,padj = 0.1)
  mtext(text = seqYlabUp[count],cex = cexAxis,line = 1.7,side = 2,las=0)
  mtext(text = seqXlabUp[count],cex = cexAxis,line = 1.7,side = 3 ,las=0)
  lines(logist(totRBF(rangx,centers,sigSquar,weightsAct),alpha=0,beta=1)~rangx,
        col=1,lwd=3,lty=2)
  # text(x=0.5,y=-0.015,labels = paste0("time=",unique(evolStats$time)[genC]/1000),
  #      cex=2)
  par(plt=posPlot(numplotx = 4,numploty = 3,idplotx = count,idploty = 1,
                  lowboundx = 8,lowboundy = 10,
                  upboundy = 90), las=1,new=TRUE)

  # meansClustmp<-tempPop[,.(alphaMean=mean(alpha),betaMean=mean(beta)),by=orderClus]
  # reacNormpClust<-sapply(meansClustmp[,orderClus], function(x){
  #   logist(rangx,alpha = meansClustmp[orderClus==x,alphaMean],
  #          beta = meansClustmp[orderClus==x,betaMean])})
  # matplot(x = rangx,y = reacNormpClust,col=colRuns[meansClustmp$orderClus],
  #          type='l',cex.axis=cexAxis,
  #          xlab="",ylab="",ylim=c(0,1),lty=1,
  #          lwd=2,yaxt=seqYax[count],xaxt="s",cex.lab=cexAxis)
  reacNormInd<-sapply(tempPop[indId %in%randInds,indId], function(x){
    logist(rangx,alpha = tempPop[indId==x,alpha],
           beta = tempPop[indId==x,beta])})
  matplot(x = rangx,y = reacNormInd,
          type='l',cex.axis=cexAxis,
          xlab="",ylab="",ylim=c(0,1),lty=1,col=1,
          lwd=2,yaxt=seqYax[count],xaxt="s",cex.lab=cexAxis)
  mtext(text = seqYlabDown[count],cex = cexAxis,line = 1.5,side = 2,las=0)
  mtext(text = seqXlabDown[count],cex = cexAxis,line = 1.5,side = 1,las=0)

  }

rm(list=grep("temp",ls(),value = T))
```

@@

# knitr::include_graphics(here("Simulations","nIntGroupNormQual_","evolDyn7_nIntGroup2000.png"))
val<-2
fileId<-val

paramName<-list.files(here("Simulations",paste0(scenario,"_")))
paramName<-grep(".json",paramName,value=TRUE) %>% grep(pattern = "*s0_*",value = TRUE)

param<-fromJSON(here("Simulations",paste0(scenario,"_"),paramName[2]))

evolList_runs<-grep(paste0(param$namParam,param$rangParam),
                    evolList,value =TRUE)
indList_runs<-grep(paste0(param$namParam,param$rangParam),
                   indList,value =TRUE)

evol<-do.call(rbind,lapply(evolList_runs,fread))
pop<-do.call(rbind,lapply(indList_runs, fread))

Valpar<-param$rangParam

nampar<-param$namParam

nCenters<-param$nCenters
sigSquar<-param$sigSq

# Aesthetic paremeters ---------------------------------------------------------

## Calculate clustering for all generations  -------------------
